\documentclass[accentcolor=tud2d,12pt,paper=a4,colorbacktitle]{tudexercise}

\usepackage[utf8]{inputenc}
\usepackage{ngerman}
\usepackage{enumerate}

\title{Code Review}
\subtitle{BonfireChat}
\subsubtitle{Bachelorpraktikum 2015}

\begin{document}

  \maketitle

  \begin{enumerate}[ 1.]
    \item Is the functionality correct?
    \item Are the classes, functions and variables named suitably?
    \item Is the class structure well designed and meeting all requirements or does it need improvements?
    \item Are there classes which have become obsolete because of a new implementation?
    \item Are there unnecessary overloaded functions or constructors?
    \item Is the perstistent database structure well designed?
    \item Does it contain functions that can be reused later? Are they placed in a Helper class?
    \item Are existing helper functions being used? Is no duplicate functionality implemented?
    \item Are all the input arguments being validated?
    \item How will the functionalities affect the performance of the app - power usage, time and memory?
    \item Is it absolutely necessary to run it on UI thread or would a background thread suffice?
    \item Are all possible failures handled?
    \item Does it degrade gracefully in case of unknown failures?
    \item Are the best practices for app development, according to Android lint, being followed?
    \item What pieces of the component can be executed in parallel?
    \item Are the operations thread-safe if they need to be?
    \item Is the layout suitable for all screen dimensions?
    \item Do all methods and fields have the proper access modifiers?
  \end{enumerate}

\end{document}
